Hypertension and microbiome

### 2019-04-29 articletwo.Rmd
Renamed var

maas.all.pairs <- expand.grid(Feature = maas.results.df.signf %>% pull(Feature),
                         Name = maas.results.df.signf %>% pull(Name))
maas.tables.df <- merge(maas.results.df.signf,
                   all.pairs,
                   all.y=TRUE,
                   by.y=c('Feature', 'Name'),
                   by.x=c('Feature', 'Name'))

>>>>

maas.all.pairs <- expand.grid(Feature = maas.results.df.signf %>% pull(Feature),
                         Name = maas.results.df.signf %>% pull(Name))
maas.tables.df <- merge(maas.results.df.signf,
                        maas.all.pairs,
                        all.y=TRUE,
                        by.y=c('Feature', 'Name'),
                        by.x=c('Feature', 'Name'))
